The impact of cosmic variance on simulating weak lensing surveys

### 2014-09-22 Writeup/paper_v3.tex
S1,S2,S3 added in the beginning of Results

\section{Results}
\label{S:results}
Having identified the overdense and underdense regions in a volume-limited sample (\S\ref{sub:overdensities}, \S\ref{sub:volumelimiting}), we will now see in this section if the morphological
parameters of the galaxies, listed in \S\ref{sub:axisratio}, have any dependence on the environment that they reside in. We have 3 different ways of volume-limiting our sample
\begin{enumerate}
 \item no redshift evolution of luminosity cut
 \item use $B$-band evolution rate for $I$-band luminosities
 \item impose stellar mass cuts instead of luminosity
\end{enumerate}
and we will present our results in each of the 3 cases. 
\rachel{Say how this connects to the 3 samples S1, S2, and S3 that you
  defined earlier.}

>>>>

\section{Results}
\label{S:results}
Having identified the overdense and underdense regions in a volume-limited sample (\S\ref{sub:overdensities}, \S\ref{sub:volumelimiting}), we will now see in this section if the morphological
parameters of the galaxies, listed in \S\ref{sub:axisratio}, have any dependence on the environment that they reside in. We have 3 different ways of volume-limiting our sample
\begin{enumerate}
 \item no redshift evolution of luminosity cut $(\s1)$,
 \item use $B$-band evolution rate for $I$-band luminosities $(\s2)$,
 \item impose stellar mass cuts instead of luminosity $(\s3)$
\end{enumerate}
and we will present our results in each of the 3 cases. 
\rachel{Say how this connects to the 3 samples S1, S2, and S3 that you defined earlier.} \arun{Done.}
